Oregon 2013 Medication for Beta-2 agonists

### 2017-07-20 r_scripts/analysis/oregon_medication.Rmd
Update oregon_medication.Rmd

plot_ts <- ggplot(or_ndc_county_ts, aes(y =rate_per_100k, x = date)) +
           geom_jitter() +
           ylab("Rate of 100k of Beta2 agonist fills") +
           xlab("Year 2013")

@@

plot_county <- ggplot(or_ndc_county_ts, aes(y =rate_per_100k, x = date)) +
               geom_jitter() + facet_wrap(~county) +
               ylab("Rate of 100k of Beta2 agonist fills")

@@

plot_health_smk <- ggplot(or_ndc_county_ts, aes(x = geo_smk_pm10, y = log(rate_per_100k+0.1))) +
  geom_point() + 
  # geom_point(aes(colour = c("red")), alpha = 0.2,  size = 1) + 
  # scale_colour_manual(values = c("red", "blue")) +
  # truncated y axis
  #scale_y_continuous(limits = c(0, 1.5)) +
  # facet_wrap(~county, scale  = "free") +
  ylab("Log Beta 2 agonists Rate per 100,000 Persons") +
  xlab("GWR Smoke PM2.5 per 10ug/m^3") +
  theme_bw()

@@

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle("Oregon: 2013 Fire Season Smoke PM2.5") +
  ylab("Smoke PM2.5 ug/m^3") +
  xlab("Year: 2013") +
  theme_bw()

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = pm_method, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Smoke Estimation Method') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

@@

DLestimate$lag <- -7:0
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw()
p

@@

plot_rr <- ggplot(rr_df, aes(x=lag, y = rel_risk)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower_95, ymax=upper_95), width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle = 90, vjust = .75)) +
  ylab("Relative Risk") +
  xlab("Outcome") +
  ggtitle("Relative Risk for a 10ug/m^3 increase PM2.5 estimated via GWR Smoke")

>>>>

plot_ts <- ggplot(or_ndc_county_ts, aes(y =rate_per_100k, x = date)) +
           geom_jitter() +
           ylab("Rate of 100k of Beta2 agonist fills") +
           xlab("Year 2013") +
           ggtitle("Oregon: 2013 Fire Season Pharmacy Fills")

@@

plot_county <- ggplot(or_ndc_county_ts, aes(y =rate_per_100k, x = date)) +
               geom_jitter() + facet_wrap(~county) +
               ylab("Rate of 100k of Beta2 agonist fills") +
               ggtitle("Oregon: 2013 Fire Season Pharmacy Fills by County")

@@

plot_health_smk <- ggplot(or_ndc_county_ts, aes(x = geo_smk_pm10, y = log(rate_per_100k+0.1))) +
  geom_point() + 
  # geom_point(aes(colour = c("red")), alpha = 0.2,  size = 1) + 
  # scale_colour_manual(values = c("red", "blue")) +
  # truncated y axis
  #scale_y_continuous(limits = c(0, 1.5)) +
  # facet_wrap(~county, scale  = "free") +
  ylab("Log Beta 2 agonists Rate per 100,000 Persons") +
  xlab("GWR Smoke PM2.5 per 10ug/m^3") +
  ggtitle("Regression of Pharmacy Fills on GWR Smoke Concentration") +
  theme_bw()

@@

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle("Oregon: 2013 Fire Season Smoke PM2.5") +
  ylab("Smoke PM2.5 ug/m^3") +
  xlab("Year 2013") +
  theme_bw()

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = pm_method, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Overall') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

DLestimate$lag <- 0:lag_max
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw() + xlab("lagged days of events") + ylab("Odds Ratio for 10ug/m^3 Increase in PM2.5")
p

@@

DLestimate$lag <- -7:0
p <- ggplot(DLestimate, aes(x=lag, y=estimate, ymin=lower, ymax=upper))
p <- p + geom_ribbon(alpha=.5) + geom_line(size=2)
p <- p + geom_line(aes(x=lag), linetype=2, size=2)
p <- p + theme_bw() + xlab("lagged days of events") + ylab("Odds Ratio for 10ug/m^3 Increase in PM2.5")
p

@@

plot_rr <- ggplot(rr_df, aes(x=lag, y = rel_risk)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower_95, ymax=upper_95), width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle = 90, vjust = .75)) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Outcome") +
  ggtitle("Relative Risk for a 10ug/m^3 increase PM2.5 estimated via GWR Smoke")
